---
title: "Exam 3"
author: "James"
date: "4/11/2020"
output: html_document
theme: superhero
number_sections: TRUE
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

<style>
div.blue { background-color:#78bdcf; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">



<style>
div.lightblue { background-color:#d7f3fa; border-radius: 5px; padding: 20px;}
</style>
<div class = "lightblue">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This is how I did exam 3
#### for Data Analysis
***
***

First, load the packages and the data:
```{r, message=FALSE,warning=FALSE,echo=TRUE}
library(tidyverse)
library(GGally)
library(modelr)
library(sjPlot)
library(dplyr)
data("mtcars")
```


Next,look at the data:
```{r,message=FALSE,warning=FALSE}
ggpairs(mtcars)
```



This looks like a lot of data. We are trying to find possible relationships between __mpg__ and the other variables. We use the *sort* function to show the correlation values between the given variables:

```{r,message=FALSE}
sort(cor(mtcars)[1,])
```
We can see that __wt__ and __cyl__ are signicicant (although they are negative, meaning that when __mpg__ goes up, both __wt__ and __cyl__ go down).

##### What does it mean when we say they are signicifant?
The correlation coefficient r measures the strength and direction of a linear relationship between two variables on a scatterplot. The value of r is always between +1 and -1. 

* 1 = a perfectly linear, positive relationship
* 0 = no relationship
* -1 = a perfectly linear, negative relationship

***

#### Now, get the p-value

The cor.test function returns several values, including the p-value from the test of significance.

* p < 0.05 = the correlation is likely significant
* p > 0.05 indicates it is not


```{r, message=FALSE,warning=FALSE}
cortest <- cor.test(mtcars$mpg, as.numeric(mtcars$wt))
cortest$p.value; cortest$conf.int
```

From the above result it is seen that the p-value is 1.293 × 10^-10. This is much less than 0.05; hence, significant corelation.

We will also run this test for the __cyl__ variable:
```{r,message=FALSE,warning=FALSE}
cortest <- cor.test(mtcars$mpg, as.numeric(mtcars$cyl))
cortest$p.value; cortest$conf.int
```
Again, the small p-value indicates that it is significant.

***

So, we will be using the column __mpg__ as our dependent variable (y-axis) and build a quick plot showing its relationship to __wt__ and __cyl__:
```{r,message=FALSE,warning=FALSE}
ggplot(mtcars, aes(x=wt,y=mpg,color=cyl)) +
  geom_point() +
  geom_smooth(method="lm",se=FALSE) +
  theme_minimal()
```


Looks like there is a relationship between __hp__ and __mpg__, and that this varies based on __cyl__. Let's build a simple model:
```{r,message=TRUE,warning=FALSE}
mod <- glm(data=mtcars,formula = mpg ~ wt * cyl)
mod
```

Before moving on, let's create another model, swapping __hp__ with __cyl__ and compare it 
```{r,message=TRUE,warning=FALSE}
mod2 <- glm(data=mtcars,formula = mpg ~ wt * hp)
mod2
```

Let's also look at their summaries in order to compare the R^2 values

```{r,message=TRUE}
summary(lm(mod))$r.squared
```

```{r,message=TRUE}
summary(lm(mod2))$r.squared
```




* R Squared for model 1 = 0.86
* R Squared for model 2 = 0.88

#### What does this mean?
Interpreting the R squared value, we say that model 1 explains 86% of the variance, whereas model 2 explains 88% of the variance. Thus, model 2 is a more accurate measure for predicting mpg, and we should continue onward with using model 2. 

###### This is a bit of a over-simplification, as a high R-squared value is not necessarily an accurate representation of reality. Similarly, a low value isn't necessarily bad either. It all depends on the data set!



Use the modelr package to make predictions from our model. Pipe that new data frame straight into ggplot to compare reality with the model predictions:
```{r,warning=FALSE,message=FALSE}
add_predictions(mtcars,mod2) %>%
  ggplot(aes(x=wt)) +
  geom_point(aes(y=pred),color="Red",shape=2) +
  geom_point(aes(y=mpg,color=hp))
```



### So what?

We can see most of the predicted values are relatively close. Well, it at least follows a the negative trend... Was our model perfect? No. Was it horrible? Dr. Zahn might think so. But I think it looks okay. 
